CS6999 Web Data and Text Mining:\\Parallel Text Indexer Project Report

### 2011-09-07 report/report.tex
Submitted
Added parallelization diagram

\begin{figure}
  \begin{center}
        \includegraphics[width=\textwidth,height=!]{parserclassdiagram}
  \end{center}
  \caption{Parser class diagram}
  \label{fig:parserclassdiagram}
\end{figure}

\begin{figure}
  \begin{center}
        \includegraphics[width=\textwidth,height=!]{parsersequencediagram}
  \end{center}
  \caption{Parser sequence diagram}
  \label{fig:parsersequencediagram}
\end{figure}

@@

Finally we will do a time comparison between our indexer
implementation and a na\"{i}ve implementation. All the time
complexities tests are  
done on a single computer and it is important to understand that all
these processes can be parallelized. A future work would be to install
our indexer on multiple computers and explore the performance gain of
running parallel instances simultaneously on all these computers.

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildsm}
  \end{figure}

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildindex}
    \end{center}
    \caption{Time to build the inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildindex}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{corpsizetimecomplexbuildindex}
  \end{center}
    \caption{Time to build the inverted index as a function of the
      size of the corpus. Time taken is shown in milliseconds on the
      y-axis and the number of documents in the collection on the
      x-axis} 
    \label{fig:corpsizetimecomplexbuildindex}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{corpsizespacecomplexbuildindex}
  \end{center}
    \caption{Size of index as a function of the size of the
      corpus. The number of database rows used to store the index is
      shown on the y-axis and the number of documents in the
      collection on the x-axis} 
    \label{fig:corpsizespacecomplexbuildindex}
\end{figure}

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the x-axis}
    \label{fig:docsizetimecomplexbuildsm}
  \end{figure}

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildindex}
    \end{center}
    \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the x-axis} 
    \label{fig:docsizetimecomplexbuildindex}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{docsizespacecomplexbuildindex}
  \end{center}
  \caption{Size of index as a function of the average document
    size. The number of database rows used to store the index is
      shown on the y-axis and the average document size in characters
      on the x-axis}  
  \label{fig:docsizespacecomplexbuildindex}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivedocumentsize}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in miliseconds on the
      y-axis and the average document size in characters on the x-axis}
  \label{fig:naivedocumentsize}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivedocumentsizelog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the
      logarithmic x-axis}
  \label{fig:naivedocumentsizelog}
\end{figure}

\subsubsection{Number of Keywords}
As expected, the two implementations exhibit a linear response to the
number of keywords used. In the na\"{i}ve implmementation:

@@

The experiment results are shown in figure \ref{fig:naivedocumentsize}
and on a logarithmic scale in figure \ref{fig:naivedocumentsizelog}.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywords}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
  \label{fig:naivenumkeywords}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywordslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the logarithmic x-axis}
  \label{fig:naivenumkeywordslog}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpus}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      milliseconds on the y-axis and the number of documents on the
      x-axis} 
  \label{fig:naivesizecorpus}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpuslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      milliseconds on the y-axis and the number of documents on the
      logarithmic x-axis} 
  \label{fig:naivesizecorpuslog}
\end{figure}

>>>>

\begin{figure}[h!]
  \begin{center}
        \includegraphics[width=\textwidth,height=!]{parserclassdiagram}
  \end{center}
  \caption{Parser class diagram}
  \label{fig:parserclassdiagram}
\end{figure}

\begin{figure}[h!]
  \begin{center}
        \includegraphics[width=\textwidth,height=!]{parsersequencediagram}
  \end{center}
  \caption{Parser sequence diagram}
  \label{fig:parsersequencediagram}
\end{figure}

@@

Finally we will do a time comparison between our indexer
implementation and a na\"{i}ve implementation. All the time
complexities tests are done on a single computer and it is important
to understand that all these processes can be parallelized. In section
\ref{parallelization} we install our indexer on multiple computers and
explore the performance gain of running parallel instances
simultaneously.

@@

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildsm}
  \end{figure}

@@

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildindex}
    \end{center}
    \caption{Time to build the inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildindex}
  \end{figure}

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{corpsizetimecomplexbuildindex}
  \end{center}
    \caption{Time to build the inverted index as a function of the
      size of the corpus. Time taken is shown in milliseconds on the
      y-axis and the number of documents in the collection on the
      x-axis} 
    \label{fig:corpsizetimecomplexbuildindex}
\end{figure}

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{corpsizespacecomplexbuildindex}
  \end{center}
    \caption{Size of index as a function of the size of the
      corpus. The number of database rows used to store the index is
      shown on the y-axis and the number of documents in the
      collection on the x-axis} 
    \label{fig:corpsizespacecomplexbuildindex}
\end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the x-axis}
    \label{fig:docsizetimecomplexbuildsm}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildindex}
    \end{center}
    \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the x-axis} 
    \label{fig:docsizetimecomplexbuildindex}
  \end{figure}

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{docsizespacecomplexbuildindex}
  \end{center}
  \caption{Size of index as a function of the average document
    size. The number of database rows used to store the index is
      shown on the y-axis and the average document size in characters
      on the x-axis}  
  \label{fig:docsizespacecomplexbuildindex}
\end{figure}

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivedocumentsize}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in miliseconds on the
      y-axis and the average document size in characters on the x-axis}
  \label{fig:naivedocumentsize}
\end{figure}

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivedocumentsizelog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the
      logarithmic x-axis}
  \label{fig:naivedocumentsizelog}
\end{figure}

\subsubsection{Number of Keywords}
As expected, the two implementations exhibit a linear response to the
number of keywords used. In the na\"{i}ve implemementation:

@@

The experiment results are shown in figure \ref{fig:naivenumkeywords}
and on a logarithmic scale in figure \ref{fig:naivenumkeywordslog}.

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywords}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
  \label{fig:naivenumkeywords}
\end{figure}

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywordslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the logarithmic x-axis}
  \label{fig:naivenumkeywordslog}
\end{figure}

@@

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpus}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      milliseconds on the y-axis and the number of documents on the
      x-axis} 
  \label{fig:naivesizecorpus}
\end{figure}

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpuslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      milliseconds on the y-axis and the number of documents on the
      logarithmic x-axis} 
  \label{fig:naivesizecorpuslog}
\end{figure}

%----------------------------------------
% Parallelization
%----------------------------------------
\subsection{Parallelization}
\label{parallelization}

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{paralleldeploymentmodel}
  \end{center}
  \caption{Deployment model of parallel indexer} 
  \label{fig:paralleldeploymentmodel}
\end{figure}
